
\documentclass[11pt,letterpaper]{article}

% Essential packages
\usepackage[margin=0.7in]{geometry}
\usepackage{array}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{ragged2e}


% Define colors - Professional tech colors
\definecolor{primary}{RGB}{0, 79, 128}    % Deep blue
\definecolor{secondary}{RGB}{50, 120, 180}  % Medium blue
\definecolor{accent}{RGB}{120, 170, 217}   % Light blue
\definecolor{lightgray}{RGB}{245, 245, 245}
\definecolor{darkgray}{RGB}{80, 80, 80}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=secondary,
    pdftitle={Software Engineer Resume},
    pdfauthor={Jane Doe}
}

% Set page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% Section formatting
\titleformat{\section}
  {\Large\bfseries\color{primary}}
  {}{0em}{}
  [{\color{primary}\titlerule[1pt]}]
\titlespacing*{\section}{0pt}{12pt}{6pt}

\titleformat{\subsection}
  {\bfseries\color{secondary}}
  {}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

% Custom commands
\newcommand{\headerName}[1]{{\fontsize{22pt}{24pt}\selectfont\textbf{\textcolor{primary}{#1}}}}
\newcommand{\headerTitle}[1]{{\fontsize{14pt}{16pt}\selectfont\textcolor{secondary}{#1}}}

\newcommand{\jobTitle}[2]{
  \textbf{\textcolor{primary}{#1}} \hfill \textit{#2}\\
}

\newcommand{\companyInfo}[2]{
  \textit{#1} \hfill #2\\
}

\newcommand{\bulletItem}[1]{
  \item #1
}

\newcommand{\customBullets}[1]{
  \begin{itemize}[leftmargin=*,label=\textcolor{secondary}{\scriptsize\textbullet},itemsep=2pt,parsep=0pt]
    #1
  \end{itemize}
}

\setlength{\parindent}{0pt}


\begin{document}

% Header section
\begin{minipage}[t]{0.6\textwidth}
    \headerName{Jane Doe}\\[4pt]
    \headerTitle{Python Developer}\\[4pt]
    % \textcolor{darkgray}{Backend Systems \& Distributed Computing Specialist}
  \end{minipage}
  \begin{minipage}[t]{0.4\textwidth}
    \begin{flushright}
      \begin{tabular}{rl}
        \textcolor{primary}{\faEnvelope} & jane.doe@example.com \\
        \textcolor{primary}{\faPhone} & +1-555-123-4567 \\
        \textcolor{primary}{\faMapMarker} & Anytown, USA\\
        \textcolor{primary}{\faLinkedin} & \url{linkedin.com/in/janedoe} \\
        \textcolor{primary}{\faGithub} & \url{github.com/janedoe}
      \end{tabular}
    \end{flushright}
  \end{minipage}

  \vspace{10pt}
  \begin{center}
  \begin{tikzpicture}
  \draw[primary, fill=primary] (0,0) rectangle (\textwidth,1.5pt);
  \end{tikzpicture}
  \end{center}
  \vspace{4pt}


% Professional summary
\section{PROFESSIONAL SUMMARY}
Results-oriented Python Developer with experience in designing, developing, and maintaining scalable applications using Flask and other modern technologies. Proven ability to collaborate effectively within teams, deliver high-quality code, and solve complex problems. Passionate about leveraging new technologies to build innovative products and exceed user expectations.

% Skills section
\section{TECHNICAL SKILLS}

\begin{multicols}{2}

    \subsection{Languages}
    \customBullets{
      \bulletItem{Python}
      \bulletItem{JavaScript}
      \bulletItem{SQL}
    }
    \subsection{Frameworks}
    \customBullets{
      \bulletItem{Flask}
      \bulletItem{React}
      \bulletItem{RESTful APIs}
    }
    \columnbreak
    \subsection{Tools}
    \customBullets{
      \bulletItem{Git}
      \bulletItem{Docker}
      \bulletItem{AWS}
    }
    \subsection{Databases}
    \customBullets{
      \bulletItem{PostgreSQL}
      \bulletItem{MySQL}
    }
\end{multicols}

\section{PROFESSIONAL EXPERIENCE}

\jobTitle{Software Engineer}{2023-01 to Present}
\companyInfo{Tech Solutions Inc.}{Anytown, USA}
\customBullets{
  \bulletItem{Developed and maintained RESTful APIs using Flask to support core application functionality.}
  \bulletItem{Collaborated with a team of engineers to design and implement new features for a web-based platform.}
  \bulletItem{Implemented CI/CD pipelines using Git and Jenkins to automate software deployment.}
  \bulletItem{Utilized AWS services such as EC2 and S3 to deploy and manage applications in the cloud.}
  \bulletItem{Wrote unit and integration tests to ensure code quality and reliability.}
  \bulletItem{Participated in code reviews to maintain coding standards and best practices.}
}

\vspace{8pt}
\jobTitle{Junior Developer}{2021-06 to 2022-12}
\companyInfo{Startup Co.}{Anytown, USA}
\customBullets{
  \bulletItem{Assisted in the development of a web application using Python and Flask.}
  \bulletItem{Contributed to the design and implementation of database schemas using PostgreSQL.}
  \bulletItem{Wrote Python scripts to automate data processing tasks.}
  \bulletItem{Participated in team meetings and contributed ideas to improve the development process.}
}

\vspace{8pt}
% Projects section
\section{NOTABLE PROJECTS}

\jobTitle{Personal Portfolio Website}{2022-02 to 2022-03}
\companyInfo{example.com/portfolio}{Web Application}
\customBullets{
  \bulletItem{Developed a personal portfolio website using React and Flask.}
  \bulletItem{Implemented a RESTful API to manage blog posts and other content.}
  \bulletItem{Deployed the website to a cloud platform using Docker and Kubernetes.}
}
\vspace{8pt}
% Education section
\section{EDUCATION}

\jobTitle{Bachelor of Science in Computer Science}{2017-09 to 2021-05}
\companyInfo{University of Anytown}{3.8}
\customBullets{
  \bulletItem{Relevant coursework: Data Structures and Algorithms, Database Management Systems, Software Engineering.}
  \bulletItem{Dean's List: Fall 2019, Spring 2020, Fall 2020, Spring 2021}
}
\vspace{4pt}
% Certifications section
\section{CERTIFICATIONS \& ACHIEVEMENTS}
\begin{multicols}{2}
\customBullets{
  \bulletItem{AWS Certified Cloud Practitioner}
}

\columnbreak

\customBullets{
  \bulletItem{Awarded 'Employee of the Month' at Tech Solutions Inc. (July 2023)}
}
\end{multicols}


\vspace{-0.3cm}
\begin{center}
\textit{\textcolor{secondary}{References available upon request}}
\end{center}

\end{document}